KV Analysis for Performing-Articulation performances

### 2020-08-08 material/stimuli/analysis/expression/stim_a/kv.Rmd
move analysis into stimuli folder
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'KV Analysis for Performing-Dynamics performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

# include only articulation
dt_kv <- dt_kv[Condition == "performing" & Skill == "dynamics"]

@@

# for forte
for (phrase in 1:length(ls_forte2)){
  for (note in 1:length(ls_forte2[[phrase]])){
    dt_kv[RowNr == ls_forte2[[phrase]][note]]$Subcomponent <- "Forte"
  }
}

# for piano
for (phrase in 1:length(ls_piano2)){
  for (note in 1:length(ls_piano2[[phrase]])){
    dt_kv[RowNr == ls_piano2[[phrase]][note]]$Subcomponent <- "Piano"
  }
}
```

@@

```{r kv, echo = FALSE}
# For each individual
kv <- dt_kv[Subcomponent == "Forte" | Subcomponent == "Piano", .(N = length(Velocity), Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, Subcomponent)]
print(kv)
```

@@

```{r kv_bar,  echo = FALSE}
p_kv <- ggplot(data = kv, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  facet_grid(Subcomponent ~ .) +
  labs(y = "Key Velocity", subtitle = "KV: Performing-Dynamics")
p_kv
```

@@

p_kv_seq <- ggplot(data = kv_seq, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Velocity", subtitle = "KV: Performing-Dynamics(All)") +
  scale_x_continuous(breaks=seq(1,72,1))
p_kv_seq
```

#### Forte
```{r kv_seq_for, fig.width = 14, fig.height = 12, echo = FALSE}
# For each individual
dt_kv$TrialNr <- as.factor(dt_kv$TrialNr)
kv_seq_for <- dt_kv[Subcomponent == "Forte", .(N = length(Velocity), Mean = mean(Velocity)), by = .(SubNr, TrialNr, RowNr)]

@@

#### Piano
```{r kv_seq_pia, fig.width = 14, fig.height = 12, echo = FALSE}
# For each individual
dt_kv$TrialNr <- as.factor(dt_kv$TrialNr)
kv_seq_pia <- dt_kv[Subcomponent == "Piano", .(N = length(Velocity), Mean = mean(Velocity)), by = .(SubNr, TrialNr, RowNr)]

@@

#### Forte
```{r kv_dis_for, fig.width = 14, fig.height = 8, echo = FALSE}
p_kv_dis_for <- ggplot(dt_kv[Subcomponent == "Forte"], aes(x = Velocity)) +
  geom_histogram(binwidth = 2, alpha = .5, position = "identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Key Velocity", y = "Count", subtitle = "KV: Performing-Dynamics(Forte)")
p_kv_dis_for
```

#### Piano
```{r kv_dis_pia, fig.width = 14, fig.height = 8, echo = FALSE}
p_kv_dis_pia <- ggplot(dt_kv[Subcomponent == "Piano"], aes(x = Velocity)) +
  geom_histogram(binwidth = 2, alpha = .5, position = "identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Key Velocity", y = "Count", subtitle = "KV: Performing-Dynamics(Piano)")
p_kv_dis_pia
```

@@

### Valid performances (exclude outliers)
#### Forte
```{r outlier_for, echo = FALSE}
# for forte
excluded_kv_for <- kv[Subcomponent == "Forte" & Mean < kv_all[Subcomponent == "Forte"]$Mean+3*kv_all[Subcomponent == "Forte"]$SD & Mean > kv_all[Subcomponent == "Forte"]$Mean-3*kv_all$SD]
print(excluded_kv_for)
```
- The number of excluded performance: `r kv_all[Subcomponent == "Forte"]$N-nrow(excluded_kv_for)`

#### Piano
```{r outlier_pia, echo = FALSE}
# for piano
excluded_kv_pia <- kv[Subcomponent == "Piano" & Mean < kv_all[Subcomponent == "Piano"]$Mean+3*kv_all[Subcomponent == "Piano"]$SD & Mean > kv_all[Subcomponent == "Piano"]$Mean-3*kv_all$SD]
print(excluded_kv_pia)
```
- The number of excluded performance: `r kv_all[Subcomponent == "Piano"]$N-nrow(excluded_kv_pia)`

```{r export, include = FALSE}
kv_valid <- dt_kv[, .(N = length(Velocity), Mean = mean(Velocity)), .(SubNr, TrialNr)]
fwrite(kv_valid, "./kv_valid.csv")
```

>>>>

---
title: 'KV Analysis for Performing-Articulation performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

# include only articulation
dt_kv <- dt_kv[Condition == "performing" & Skill == "articulation"]

@@

# for legato
for (phrase in 1:length(ls_legato2)){
  for (note in 1:length(ls_legato2[[phrase]])){
    dt_kv[RowNr == ls_legato2[[phrase]][note]]$Subcomponent <- "Legato"
  }
}

# for staccato
for (phrase in 1:length(ls_staccato2)){
  for (note in 1:length(ls_staccato2[[phrase]])){
    dt_kv[RowNr == ls_staccato2[[phrase]][note]]$Subcomponent <- "Staccato"
  }
}
```

@@

```{r kv, echo = FALSE}
# For each individual
kv <- dt_kv[Subcomponent == "Legato" | Subcomponent == "Staccato", .(N = length(Velocity), Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, Subcomponent)]
print(kv)
```

@@

```{r kv_bar,  echo = FALSE}
p_kv <- ggplot(data = kv, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  facet_grid(Subcomponent ~ .) +
  labs(y = "Key Velocity", subtitle = "KV: Performing-Articulation")
p_kv
```

@@

p_kv_seq <- ggplot(data = kv_seq, aes(x = RowNr, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  facet_grid(SubNr ~ .) +
  labs(x = "RowNr", y = "Velocity", subtitle = "KV: Performing-Articulation(All)") +
  scale_x_continuous(breaks=seq(1,72,1))
p_kv_seq
```

#### Legato
```{r kv_seq_for, fig.width = 14, fig.height = 12, echo = FALSE}
# For each individual
dt_kv$TrialNr <- as.factor(dt_kv$TrialNr)
kv_seq_for <- dt_kv[Subcomponent == "Legato", .(N = length(Velocity), Mean = mean(Velocity)), by = .(SubNr, TrialNr, RowNr)]

@@

#### Staccato
```{r kv_seq_pia, fig.width = 14, fig.height = 12, echo = FALSE}
# For each individual
dt_kv$TrialNr <- as.factor(dt_kv$TrialNr)
kv_seq_pia <- dt_kv[Subcomponent == "Staccato", .(N = length(Velocity), Mean = mean(Velocity)), by = .(SubNr, TrialNr, RowNr)]

@@

#### Legato
```{r kv_dis_for, fig.width = 14, fig.height = 8, echo = FALSE}
p_kv_dis_for <- ggplot(dt_kv[Subcomponent == "Legato"], aes(x = Velocity)) +
  geom_histogram(binwidth = 2, alpha = .5, position = "identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Key Velocity", y = "Count", subtitle = "KV: Performing-Articulation(Legato)")
p_kv_dis_for
```

#### Staccato
```{r kv_dis_pia, fig.width = 14, fig.height = 8, echo = FALSE}
p_kv_dis_pia <- ggplot(dt_kv[Subcomponent == "Staccato"], aes(x = Velocity)) +
  geom_histogram(binwidth = 2, alpha = .5, position = "identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Key Velocity", y = "Count", subtitle = "KV: Performing-Articulation(Staccato)")
p_kv_dis_pia
```

@@

### Valid performances (exclude outliers)
#### Legato
```{r outlier_leg, echo = FALSE}
# for legato
excluded_kv_leg <- kv[Subcomponent == "Legato" & Mean < kv_all[Subcomponent == "Legato"]$Mean+3*kv_all[Subcomponent == "Legato"]$SD & Mean > kv_all[Subcomponent == "Legato"]$Mean-3*kv_all$SD]
print(excluded_kv_leg)
```
- The number of excluded performance: `r kv_all[Subcomponent == "Legato"]$N-nrow(excluded_kv_leg)`

#### Staccato
```{r outlier_sta, echo = FALSE}
# for staccato
excluded_kv_sta <- kv[Subcomponent == "Staccato" & Mean < kv_all[Subcomponent == "Staccato"]$Mean+3*kv_all[Subcomponent == "Staccato"]$SD & Mean > kv_all[Subcomponent == "Staccato"]$Mean-3*kv_all$SD]
print(excluded_kv_sta)
```
- The number of excluded performance: `r kv_all[Subcomponent == "Staccato"]$N-nrow(excluded_kv_sta)`

<!-- ```{r export, include = FALSE} -->
<!-- kv_valid <- dt_kv[, .(N = length(Velocity), Mean = mean(Velocity)), .(SubNr, TrialNr)] -->
<!-- fwrite(kv_valid, "./kv_valid.csv") -->
<!-- ``` -->
